Considering scale in multilayer animal social networks

### 2020-06-16 paper/manuscript.Rmd
last sentence of intro paragraph
last sentence P2

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through ecological processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among others. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent.

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
associations to occur individuals must share space, and thus have overlapping
home ranges [@Vander_Wal_2013]. In the context of the social environment, home
range overlap is an example of how animals share space over coarser spatial and
temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a].

>>>>

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through ecological processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among others. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent. 
<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
associations to occur individuals must share space, and thus have overlapping
home ranges [@Vander_Wal_2013]. In the context of the social environment, home
range overlap is an example of how animals share space over coarser spatial and
temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction [@Castles_2014;
@Farine_2015a]. We therefore define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
potential for adaptive variance in social relationships is also scale-dependent. 
<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
under the expectation that there is some scale at which variance is greatest, and presumably
it is this scale that has the greatest effect on fitness or other traits-->
